---
title: "Draw China Maps Using `ggplot2`"
author: "Aetna International"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: yes
---
```{r setup, include=FALSE}
Sys.setlocale("LC_CTYPE", 'Chs')
knitr::opts_chunk$set(fig.width=8, fig.height=5.5)
fn = local({  ## counter for figures
  i = 0
  function(x, chap=NULL, renum=FALSE) {
      ## params
      ## x: chart title
      ## chap: chapter number, if assigned, show "Figure chap-x""
      ## renum: if TRUE, i be set 0
    if (renum) i <<- 0
    i <<- i + 1
    paste('<b>Figure ', if (is.null(chap)) '' else paste0(chap, '-'), i, '</b>: ', 
          x, sep = '')
  }
})
tn = local({  ## counter for tables
  j = 0
  function(x, chap=NULL, renum=FALSE) {
    if (renum) j <<- 0
    j <<- j + 1
    paste('<b>Table ', if (is.null(chap)) '' else paste0(chap, '-'), j, '</b>: ', 
          x, sep = '')
  }
})
```

# Introduction

You can always use `ggplot2` to draw maps. But when it comes to China maps, you might have a difficult time in getting map data. This document is to guide you to draw province-level and city-level China maps more easily.

We provide 2 datasets containing level-1 and level-2 geodata for plotting: `cnMapL1.rds` and `cnMapL2.rds`. The meta data are `cnMapL1.csv` and `cnMapL2.csv`. 

The files are stored in `//ship-oa-001/china_health_advisory/Analytics/GUIDE And TOOLS/Guideline/files`.

## Structure of cnMapL1

The foreign key 'id' of cnMapL1 is connected with the primary key 'NAME' in meta1.

```{r mapL1 str, echo=FALSE}
fpath <- '//ship-oa-001/china_health_advisory/Analytics/GUIDE And TOOLS/Guideline/files/'
cnMapL1 <- readRDS(paste0(fpath, 'cnMapL1.rds'))
meta1 <- read.csv(paste0(fpath, 'cnMapL1.csv'), stringsAsFactors=FALSE, encoding='CP936')
str(cnMapL1)
str(meta1)
```

## Structure of cnMapL2

The foreign key 'id' of cnMapL2 is connected with the primary key 'NAME' in meta2.

```{r mapL2 str, echo=FALSE}
cnMapL2 <- readRDS(paste0(fpath, 'cnMapL2.rds'))
meta2 <- read.csv(paste0(fpath, 'cnMapL2.csv'), stringsAsFactors=FALSE, encoding='CP936')
str(cnMapL2)
str(meta2)
```

Note that there are 5 pairs of duplicated names in cnMapL2, so the id are changed a bit:

- Suzhou: 苏州 (Suzhou)、宿州 (Suzhou AH)
- Fuzhou: 福州 (Fuzhou)、抚州 (Fuzhou JX)
- Yichun: 伊春 (Yichun)、宜春 (Yichun JX)
- Yulin: 榆林 (Yulin)、玉林 (Yulin GX)
- Taizhou: 泰州 (Taizhou)、台州 (Taizhou ZJ)

## Fetch More Data

- Visit GADM site [^gadm] to get more datasets;
- Download R datasets you want;
- Use `readRDS` to read the S4 object from the rds file;
- Use `broom::tidy` function to extract polygon data from the S4 object;
- `<object name>@data` is the meta data.

[^gadm]: http://http://gadm.org/ "Global Administrative Areas"

Note that the GADM certificate forbids commercial use. 

# Base Map

Both `geom_map` and `geom_polygon` can be used to plot maps [^ggplot2].

[^ggplot2]: Refer to ggplot2 official manual at http://docs.ggplot2.org.

## Level-1 Base Map

Use dataset `cnMapL1` to draw a level-1 China base map.

```{r L1 basemap, fig.cap=fn('China Base Map - Province Level')}
library(ggplot2)
g <- ggplot(data=cnMapL1, aes(map_id=id)) + 
    geom_map(map=cnMapL1, fill='white', colour='lightgray') +
    expand_limits(x=cnMapL1$long, y=cnMapL1$lat)
g
```

The syntax could also be:

```r
ggplot() + 
    geom_map(aes(map_id=id), data=cnMapL1, map=cnMapL1, fill='white', 
        colour='lightgray') +
    expand_limits(x=cnMapL1$long, y=cnMapL1$lat)
```

You can apply `projection = 'albers'` or `polyconic`.

```{r L1 basemap proj, fig.cap=fn("China Base Map with Albers Projection - Province Level")}
g + coord_map(projection = 'albers', lat0 = 25, lat1 = 45)
```

You can attach `meta1` dataset to show the name labels of the provinces.

```{r L1 basemap with lab, fig.cap=fn('China Base Map with Labels - Province Level')}
g <- ggplot(meta1, aes(map_id=NAME)) +
    geom_map(aes(map_id=id, group=group), data=cnMapL1, map=cnMapL1, fill='white', 
        colour='lightgray') +
    expand_limits(x=cnMapL1$long, y=cnMapL1$lat) +
    geom_text(aes(x=PTX, y=PTY, label=NAME_LAB), size=3, colour="gray")
g
```

## Level-2 Base Map

```{r L2 basemap geom_map, fig.cap=fn('China Base Map - City Level')}
g <- ggplot(data=cnMapL2, aes(map_id=id)) + 
    geom_map(map=cnMapL2,  fill='white', colour='lightgray') +
    expand_limits(x=cnMapL2$long, y=cnMapL2$lat) + xlab('Long') + ylab('Lat')
g
```

It is the same with 

```r
ggplot() + geom_polygon(data=cnMapL2, aes(x=long, y=lat, group=group), 
                        fill='white', colour='lightgray')
```

## Mixed Base Map

By stacking geom_polygons, you can get two layers of borders.

```{r mixed basemap, fig.cap=fn('China Base Map - Province & City Level')}
g <- ggplot() + geom_polygon(data=cnMapL2, aes(x=long, y=lat, group=group), 
                             fill='white', colour='lightgray', size=0.2)
g <- g + geom_polygon(data=cnMapL1, aes(x=long, y=lat, group=group), 
                 color='darkgray', alpha=0)
g
```

## Partial Base Map

You can also extract part of China to draw a map.

```{r sub basemap, fig.cap=fn('China Base Map with Labels - GD, HK & MC')}
part.prov <- c('Guangdong', 'Hong Kong', 'Macao')
part.data <- meta2$NAME[meta2$NAME_1 %in% part.prov]
submap <- cnMapL2[cnMapL2$id %in% part.data,]
g <- ggplot(meta2[meta2$NAME_1 %in% part.prov,]) + 
    geom_polygon(data=submap, aes(x=long, y=lat, group=group), 
                 fill='white', colour='gray', size=0.2)
g <- g + geom_text(aes(x=PTX, y=PTY, label=NAME_LAB), size=3, color='darkgray') + 
    coord_equal()
g
```

# Scatter Plot on Map

Use embedded dataset 'world.cities' in `maps` to draw a scatterplot.

```{r pop data, fig.cap=fn('Big Cities of China on Cartesian Coordinate System')}
library(maps)
data('world.cities')
big.cities <- world.cities[world.cities$country.etc %in% c('China', 'Taiwan'),]
ggplot(big.cities, aes(x=long, y=lat, size=pop)) + 
    geom_point(color='red', alpha=0.3)
```

> Note that `geom_map` and `geom_polygon` apply WGS coordinate system. So if you have some data from Baidu, you should use `convBD2WGS` function in `asehms` package to convert the coordinates.


We have got a scatterplot in cartesian coordinate system. Now let's plot it on top of the base map.

```{r scatter on basemap, fig.cap=fn('Big Cities of China')}
big.cities$capital <- as.factor(big.cities$capital)
levels(big.cities$capital) <- c('City', 'Capital', 'Municipality', 'Province capital')
g <- ggplot(big.cities, aes(x=long, y=lat, size=pop)) + 
    geom_polygon(data=cnMapL1, aes(x=long, y=lat, group=group), fill='white',
                 color='gray85', size=0.2) +
    geom_point(aes(color=capital), alpha=0.5) + coord_map()
g
```

Put a gray layer beneath the plot, to render the plot more '3-D'.

```{r 3d scatter, fig.cap=fn('Big Cities of China - Shadow 3D')}
g <- ggplot(big.cities, aes(x=long, y=lat, size=pop, color=capital)) + 
    geom_polygon(data=cnMapL1, aes(x=long + 0.7, y=lat-0.5, group=group), 
                 color='grey50', size=0.2, fill='grey50') + 
    geom_polygon(data=cnMapL1, aes(x=long, y=lat, group=group), fill='white',
                 color='gray85', size=0.2) + 
    geom_point(alpha=0.5) + coord_map()
g
```

# Choropleth Plot

Use area of each city to plot a choropleth plot.

We need to merge meta data and map data before plotting the choropleth. Note that you always need to type `group=group` in `aes` mapping parameter in the initiation command `ggplot()`.

```{r choropleth, fig.cap=fn('Size of China Cities')}
area.map <- merge(cnMapL2, meta2[,c("NAME", "AREA")], 
                  by.x="id", by.y="NAME", sort=FALSE)
g <- ggplot(area.map, aes(x=long, y=lat, group=group, fill=AREA)) +
    geom_polygon(color='white', size=0.05) +
    scale_fill_gradient(low='skyblue', high='darkgreen') +
    theme_minimal() + coord_map('polyconic') 
g
```

# References
